Electricity Usage in Toronto’s Public Facilities: Analyzing the Impact of Building Size on Energy Consumption

### 2024-09-27 paper/paper.qmd
updated

##install the packages
##install.packages("opendatatoronto")
##install.packages("tidyverse")
##install.packages("knitr")

@@

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| fig-cap: "Regression of Electricity Use on Area"
#| warning: false

library(ggplot2)

annual_energy_consumption_data_2021 <- analysis_data %>%
  mutate(log_Area = log(Area), log_kWh = log(kWh))

ggplot(annual_energy_consumption_data_2021, aes(x = log_Area, y = log_kWh)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  ggtitle("Log-Log Regression of Electricity Use on Area") +
  xlab("Log of Area (m²)") +
  ylab("Log of Electricity Use (kWh)") +
  theme_minimal()

>>>>

##install the packages
# install.packages("opendatatoronto")
# install.packages("tidyverse")
# install.packages("knitr")

@@

Our results are summarized in @fig-modelresults.

```{r}
#| label: fig-modelresults
#| fig-cap: Regression of Electricity Use on Area
#| echo: false
#| message: false
#| warning: false

raw_data <- read.csv(here::here("data/raw_data/raw_data.csv"), skip=5)
analysis_data <- read.csv(here::here("data/analysis_data/analysis_data.csv"))

annual_energy_consumption_data_2021 <- analysis_data |>
  mutate(log_Area = log(Area), log_kWh = log(kWh))

ggplot(annual_energy_consumption_data_2021, aes(x = log_Area, y = log_kWh)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, formula = y ~ x, color = "blue") +
  ggtitle("Log-Log Regression of Electricity Use on Area") +
  xlab("Log of Area (m²)") +
  ylab("Log of Electricity Use (kWh)") +
  theme_minimal()
```
